Paper figures

### 2020-10-05 notebooks/paper_plots_0909.Rmd
auc made inlet

library(MESS)
auc_data <- deletion_df%>%
    group_by(group, variable_0)%>%
    summarise(auc=MESS::auc(gc_size,range), r = range[min(which(gc_size < 0.05))])%>%
    ungroup()%>%
    mutate(variable_0=fct_reorder(variable_0, auc, min))

auc_plot <- auc_data%>%
    ggplot(aes(x=variable_0,y=auc))+
    geom_bar(aes(fill=variable_0),stat='identity')+
 #   geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
#    geom_line(aes(group=group),color='grey')+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    theme_bw()+
    ylab("Robustness")+
    xlab("Deletion parameter")+
    labs(fill = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
    scale_fill_brewer(palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='right')

#combined_df %>% group_by(data)%>%summarise(deg_btw = cor(deg, btw),
#                                           deg_eff = cor(deg,eff),
#                                           deg_sens = cor(deg,sens),
#                                           deg_eigen = cor(deg, eigenvec_centr),
#                                           deg_closeness = cor(deg, closeness_centr))
deletion_plot <- deletion_df %>% mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
    ggplot(aes(x=range, y= gc_size, color = variable_0  ))+
#    geom_point(size=1)+
        geom_line()+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('% Deleted Nodes')+
    ylab('% Giant Component Size')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    theme_bw()+
    theme(legend.position='right')

deletion_lgn <- cowplot::get_legend(auc_plot)
plot_grid(deletion_plot+    theme(legend.position='')
, auc_plot+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)

@@

```{r}
convert_networkx_to_igraph <- 			# 
    function
(
 	nx_object,
    df
)
{
    nx =  reticulate::import("networkx")
    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
    #ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
    ig = igraph::set_vertex_attr(ig , name =  'name', value  = (df$orf_name))
    #igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
    ig
}
```
```{r}
plot_network_spring <- 			# 
    function
(
    gc , df , pos , ... 	
)
{
 pcc_gc_ig = convert_networkx_to_igraph(gc, df)

png('tmp.png')
plot(pcc_gc_ig, vertex.size=1, vertex.label=NA, layout = pos)
dev.off()

}
pcc_gc = py$pcc_gc
pcc_gc_pos = matrix(unlist(py$pcc_gc_pos),ncol=2,byrow=TRUE)

pcc_gc_ig = convert_networkx_to_igraph(pcc_gc, pcc_df)

get_subnetwork  <- function(gc, subset){
    sub_gc_nodes = igraph::ego(gc, nodes= subset)%>%unlist%>%unique

    sub_gc  <- igraph::induced_subgraph(gc, sub_gc_nodes)

    sub_gc
}

pcc_sensors = pcc_df %>% filter(sens>quantile(sens,0.99))
pcc_sensor_sub = get_subnetwork(pcc_gc_ig, pcc_sensors$orf_name)
#plot_network_spring(pcc_gc, pcc_df, pcc_gc_pos)

png('tmp.png', res=150, height=3, width=3,units='in')
plot(pcc_sensor_sub, vertex.size = 2 , vertex.color = 'white', vertex.label.color='black',vertex.label.size=8, vertex.label.cex = 0.4, layout=igraph::layout.fruchterman.reingold)
dev.off()
```

>>>>

library(MESS)
auc_data <- deletion_df%>%
    group_by(group, variable_0)%>%
    summarise(auc=MESS::auc(gc_size,range), r = range[min(which(gc_size < 0.05))])%>%
    ungroup()%>%
    mutate(variable_0=fct_reorder(variable_0, auc, min))%>%pivot_wider(-r, names_from=group, values_from=auc)

auc_plot_pcc <- auc_data%>%
    ggplot(aes(x=variable_0,y=pcc))+
    geom_bar(aes(fill=variable_0,alpha = (variable_0  )),stat='identity')+
    theme_bw()+
    ylab("Robustness")+
    xlab("Deletion parameter")+
    scale_alpha_manual(name='Deletion\nparameter', values = c(0.3,0.3,1,0.3,0.3,0.3,1), labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"), guide = 'legend')+
    labs(fill = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "D",
                                "B",
                                "Eff",
                                "C",
                                "E",
                                "R",
                                "S"))+
    scale_fill_brewer(name = 'Deletion\nparameter', palette = "Set1", guide='legend', labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='bottom', legend.title=element_text(size=18), legend.text=element_text(size=14),legend.spacing.x = unit(1.0, 'cm'),legend.spacing.y = unit(1.0, 'cm'))
auc_plot_yuri <- auc_data%>%
    ggplot(aes(x=variable_0,y=yuri))+
    geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ),stat='identity')+
    theme_bw()+
    ylab("Robustness")+
    xlab("Deletion parameter")+
    labs(fill = "Deletion\nparameter")+
    scale_alpha_manual(name = '', values = c(0.3, 1), guide = FALSE)+
    scale_x_discrete(labels = c(
                                "D",
                                "B",
                                "Eff",
                                "C",
                                "E",
                                "R",
                                "S"))+
    scale_fill_brewer(name='', palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='right')
auc_plot_huri<- auc_data%>%
    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ))+
    geom_bar(aes(fill=variable_0),stat='identity')+
    theme_bw()+
    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
    ylab("Robustness")+
    xlab("Deletion parameter")+
    labs(fill = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "D",
                                "B",
                                "Eff",
                                "C",
                                "E",
                                "R",
                                "S"))+
    scale_fill_brewer(palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='right')
#combined_df %>% group_by(data)%>%summarise(deg_btw = cor(deg, btw),
#                                           deg_eff = cor(deg,eff),
#                                           deg_sens = cor(deg,sens),
#                                           deg_eigen = cor(deg, eigenvec_centr),
#                                           deg_closeness = cor(deg, closeness_centr))
deletion_plot_pcc <-  pcc_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
    ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ))+
#    geom_point(size=1)+
        geom_line(size=2)+
#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('% Deleted Nodes')+
    ylab('% Giant Component Size')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    theme_bw()+
    ggtitle('Costanzo 2016')+
    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
    theme(legend.position='bottom',panel.border = element_blank(), axis.line = element_line())
deletion_plot_yuri <-  yuri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion')  ))+
#    geom_point(size=1)+
        geom_line(size=2)+
#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('% Deleted Nodes')+
    ggtitle('Yeast PPI')+
    ylab('% Giant Component Size')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
    theme_bw()+
    theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
deletion_plot_huri <-  huri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion')  ))+
#    geom_point(size=1)+
        geom_line(size=2)+
#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('% Deleted Nodes')+
    ylab('% Giant Component Size')+
    ggtitle('HuRI')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
    theme_bw()+
    theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
deletion_lgn <- cowplot::get_legend(auc_plot_pcc)
pcc_with_inset = ggdraw(deletion_plot_pcc+    theme(legend.position=''))+
  draw_plot(auc_plot_pcc+theme(legend.position=''), .50, .62, .45, .35) +
  draw_plot_label(
    c("A", ""),
    c(0, 0.45),
    c(1, 0.95),
    size = 12
  )
yuri_with_inset = ggdraw(deletion_plot_yuri+    theme(legend.position=''))+
  draw_plot(auc_plot_yuri+theme(legend.position=''), .50, .62, .45, .35) +
  draw_plot_label(
    c("B", ""),
    c(0, 0.45),
    c(1, 0.95),
    size = 12
  )
huri_with_inset = ggdraw(deletion_plot_huri+    theme(legend.position=''))+
  draw_plot(auc_plot_huri+theme(legend.position=''), .50, .62, .45, .35) +
  draw_plot_label(
    c("C", ""),
    c(0, 0.45),
    c(1, 0.95),
    size = 12
  )
plot_grid(pcc_with_inset, yuri_with_inset, huri_with_inset, ncol=3)%>%plot_grid(deletion_lgn,nrow=2, rel_heights=c(0.9,.1))
ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)

plot_grid(deletion_plot_pcc+    theme(legend.position='')
, auc_plot_pcc+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))

@@

```{r}
convert_networkx_to_igraph <- 			# 
    function
(
 	nx_object,
    df
)
{
    nx =  reticulate::import("networkx")
    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
    #ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
    ig = igraph::set_vertex_attr(ig , name =  'name', value  = (df$orf_name))
    #igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
    ig
}
```
